Prepare Validation Data

### 2023-02-02 Code/0_PrepareValidationData.Rmd
Validation added
Comment mb.c binary

---
title: "Prepare Validation Data"
author: "Carolien C.H.M. Maas"
date: "December 2022"
output: html_document
---

@@

Set recurrence time equal to follow-up time for those without recurrence
```{r, eval=TRUE}
sel.val.data$Rec.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]<-sel.val.data$FU.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]
table(sel.val.data$Status, sel.val.data$Recurrence)
```

>>>>

---
title: "Prepare Validation Data"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

Set recurrence time equal to follow-up time for those without recurrence
```{r, eval=TRUE}
sel.val.data$Rec.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]<-sel.val.data$FU.time[sel.val.data$Recurrence=="no recurrence"|is.na(sel.val.data$SNdate)]

sel.val.data$Rec.time[sel.val.data$Recurrence=="recurrence"&is.na(sel.val.data$Date_1st_Rec)]<-NA
table(sel.val.data$Status, sel.val.data$Recurrence)
```
